%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This file was adapted from the following original:
%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

{\huge{\textbf{\href{https://github.com/neoshrew/CV/blob/master/andrew_gelnar_cv.pdf}{Andrew Gelnar}}}}
\\
\rule{\textwidth}{0.5mm}
\\
Platform Engineering Manager, London
\hfill
apgelnar@gmail.com


A seasoned cloud infrastructure professional with extensive experience leading and managing
high-performance teams.
Skilled in designing and deploying cloud infrastructure solutions, managing projects, and
ensuring compliance with industry best practices.


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------
\vspace{-5mm}
\section{Skills}

\skills{

      \skillgroup{Advanced}
      {
            AWS, Terraform, Python, Bash, SQL, Git, Databricks, Cloud architecture,
      }

      \hline

      \skillgroup{Proficient}
      {
            Docker, GitHub, Okta, CI/CD practices, SRE, Automated Testing,
            \\
            Project Management, People Management
      }

      \hline

      \skillgroup{Intermediate}
      {
            Kubernetes, Helm, Apache Kafka, Apache Spark, Redis, SQLite, Postgres, NGINX, Linux
      }

}
%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\jobheader
{March 2021}{present}
{MatchesFashion}
{Principal Platform Engineer, Engineering Manager}
{
      AWS, Databricks, spark, Terraform, GitHub, Apache Kafka, Lucid Chart, Excalidraw,
      Okta, system design, People Management, Project Management
}
{
  \begin{itemize}
      \item Managed the Data Platform team and the Network Infrastructure team, defining
            the teams' roadmaps and liaising with stakeholders in the greater tech team.
            This also involved mentoring more junior engineers expanding their skillsets
            into cloud engineering as well as Engineering Enablement practices.

      \item Sat across the entire tech department as an SME for AWS and other cloud services,
            notably advising our security functions for cloud and information security.
            Filled a partially operational role managing some of Matches'
            suite of cloud products including GCP, Okta, LastPass, and various DNS providers.

      \item Was responsible for all aspects of the Data team's cloud infrastructure and completely
            redesigned the setup of networking, IAM, and S3 to make security a core part of our use
            of these services.

      \item Lead the design of the new Databricks based Datalake, focusing on resiliency, security,
            and compliance. Designed resilient pipelines for event-driven file ingestion (using S3, SQS,
            and Lambda) and event-sourced ingestion (Apache Kafka, Databricks, and Spark).

      \item Recovered a migration project to replace VPC Peering in favour of AWS Transit Gateway,
            after all previous team members on the project resigned. Managed the integration of this
            new inter-VPC network with our corporate SD-WAN network.

      \item Reorganised the Infra team away from being a ticket-based service team to a project lead team,
            to achieve predictable and consistent delivery on project based work.

      \item Designed and managed the creation of a self-service project for the Data Engineers to speed up
            initial project creation, whilst ensuring security of CI/CD and Application setups through
            specific and least-privileged access principles. This reduced the initial setup of Databricks-based
            projects for the data engineers from up-to two weeks to a day.

  \end{itemize}
}
\jobheader
{Jul 2019}{Feb 2021}
{OakNorth}
{Head of Infrastructure}
{
      Terraform,
      AWS,
      Helm,
      Docker,
      Kubernetes,
      AzureAD,
      GitHub,
      DataDog,
      PagerDuty,
      Lucid Chart,
      system design,
      Management
}
{
  \begin{itemize}
 % As with the previous section, less sequential reads better in my opinion
 % Initially joined as an IC and got promoted to managing the infra team soon after.
 % Poeple find the Oaknorth matrix management confusing so I tend to just skip that part.
 % Lead the team to solve X, Y and Z problems - Re-build the infrastructure from the ground up,
 % splitting different customers into their own accounts with focus on security and compliance
 % Introduced CI/CD within infrastructure and decoupled from the slow and painful release process for the product
 % Also something about the team having stakeholders across all of engineering and how you handled this
      \item Initially joined as an IC in the Cloud Infrastructure team, which I subsequently managed.
            This involved working with stakeholders across all of engineering to establish the team's
            roadmap taking into account dependent teams' individual roadmaps.

      \item Rebuilt our single tenancy client platform infrastructure to have CI/CD and automated processes
            for creating and updating client environments, replacing slow and error prone manual processes.

      \item Worked closely with Security and Compliance to ensure infrastructure and applications adhered
            to industry best practices and handled client data appropriately, involving being a key
            reviewer for designs/changes involving data.

      \item Instigated and managed our access control procedures for the engineering department
            to fill a shortfall in compliance, and worked with IT to harden our security
            with better SSO integrations, and utilisation of AzureAD's auto-provisioning
            with SCIM wherever possible.

      \item Performed on call duties and worked closely with the heads of engineering and product support
            to refine our incident handling policies. Also heavily involved with our incident postmortem
            process, ensuring we performed useful and productive investigations with actionable outcomes.

  \end{itemize}
}
\jobheader
{May 2018}{Jun 2019}
{Red Ventures}
{Senior Engineer}
{
      Terraform,
      AWS,
      GCP,
      Golang,
      Kubernetes,
      Apache Kafka
}
{
      \begin{itemize}

      \item Joined to help build and run cloud infrastructure team, working
            with several engineering teams in the US to bring RV's tech stack to the EU.
            Authored and maintained reusable Terraform configuration to support migrating
            suites of microservices in AWS cloud.

      \item Migrating these systems involved working closely with the Security
            and Compliance departments from both the UK and the US to ensure they
            adhered to local UK and EU legislation (GDPR, PECR, e-privacy, etc).

      \item Created initial infrastructure for Bankrate UK's initial launch, and worked
            to migrate it from a statically generated site in AWS S3 to an application hosted
            in GCP's Kubernetes engine GKE.

      \item Moved to work with the Data Services team of our new operating partner
            (ZPG Comparison - uSwitch \& money.co.uk) following a structural change
            in the business. This involved creating a new secure real-time event
            pipeline using Apache Kafka and AWS' DynamoDB, written in Golang.

  \end{itemize}

}
\jobheader
{May 2016}{May 2018}
{Condé Nast Britain}
{Software Engineer}
{
      Python (Flask, SQLAlchemy),
      Postgres,
      Redis,
      RabbitMQ,
      Docker,
      AWS
}
{
  \begin{itemize}

      \item Responsible for backend and infrastructure taking over the migration to AWS ECS.

      \item Created new read-only API to decrease site load times. Also created and fixed
            caching site-wide using Redis to solve periodic site outages related to
            releases and cache space changes.

      \item Worked with the Product and Front-End teams to design extensible data models
            for modeling editorial content, and basic design of back-office CMS
            interfaces.

      \item Instigated new Git workflows and release processes to scale with growing
            numbers of engineers. Worked on extending our in-house build and deploy
            tool \textit{Brickyard} in support of these processes.

  \end{itemize}

}
\jobheader
{Jun 2012}{May 2016}
{Geneity Ltd. (part of Playtech Sports)}
{Software Developer}
{
      Python,
      Oracle, SQLite,
      Memcache, Redis,
      RabbitMQ,
      Bash,
      Git,
      Docker, docker-compose,
      HTML, CSS, JavaScript
}
{
      \begin{itemize}

      \item Worked on backend and APIs. Member of the the operations team providing
            1$^{\textrm{st}}$-3$^{\textrm{rd}}$ line support for all systems.

      \item conducted technical interviews, mentored new starters, and managed of a small
            development team.

      \end{itemize}
}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\textbf{BSc (Hons) in Computer Science 2:1 - The University of Manchester}
\\
\textbf{A Levels}: Maths A, Computing B, physics B, Chemistry C;
\textbf{AS Levels}: Philosophy D;
\textbf{GCSE}:
   Maths: A*,
   Statistics: A*,
   English (Lang): A,
   English (lit): B,
   Science (double award): AA,
   Music: A,
   German: A,
   IT: A,
   Religious Studies: C


% \section{Miscellaneous}

% \mytabbedblock{Awards}{
%   Quarterly performance award, Geneity Ltd. Jun 2014;
%   Excellence in customer service, Iceland Foods Ltd. 2011;
%   BTEC in aviation studies
% }

\end{document}
